\section{Prim's Algorithm}\index{graph!Prim's Algorithm}
#ifdef hackpackpp
Prim's algorithm is a greedy algorithm that allows for finding a minimum spanning tree/forest in $O(E + \log{V})$ time.
Prim's algorithm is implemented by doing the following:

\begin{enumerate}
	\item Choose an arbitrary unvisited node in the graph.
	\item Grow the tree by choosing the node that can be added to the tree by least cost.
	\item Repeat step 2 until all connected nodes have been visited. If there are still nodes, return to step 1.
\end{enumerate}

#endif
\subsection{Applications}
\begin{itemize}
	\item Finding a minimum spanning tree
\end{itemize}

#ifdef hackpackpp
\subsection{Example Contest Problem: Cow Connection}
Farmer John has not been very diligent in mowing his farm.
As a result, the grazing field now resembles a maze with small openings at the intersections.

At night, this maze is unlit, and is very dangerous.
Farmer John wants to improve safety by installing lights along paths in the maze.
However, Farmer John does not have much extra money to spend on this effort.

He would like to find a set of paths that connect all of the intersections at minimal cost, but is unsure if he can afford it.
Please help Farmer John find the cost of lighting the maze and the paths to include.
\subsubsection{Input Format}
\begin{itemize}
\item Line 1: One integer, $N$, $(N < 1000000)$ specifying the number of paths in the corn field.
\item Line 2..$(N+1)$: Each line contains three integers $S$, $D$ and $C$ where:
	\begin{itemize}
		\item $S$ and $D$ correspond to end points intersections of a given path. $0 \leq S < N$ and $0 \leq D < N$.
		\item $C$ is the cost of lighting that edge. $(0 < C < 1000000$
	\end{itemize}
\end{itemize}

\subsubsection{Sample Input}
\acmlisting[label=Cowconnection Sample Input, caption=Cowconnection Sample Input]{./algorithms/prims-algorithm/problems/cowconnection/cowconnection.in}
\subsubsection{Output Format}
\begin{itemize}
	\item Line 1: One integer, representing the minimum cost.
	\item Line 2..$(N+1)$: Two integers, the sets of intersections that are endpoints in the paths Farmer John should include. These integers should be in order from least to greatest.
\end{itemize}
\subsubsection{Sample Output}
\acmlisting[label=Cowconnection Sample Output, caption=Cowconnection Sample Output]{./algorithms/prims-algorithm/problems/cowconnection/cowconnection.out}
\subsubsection{Example Solution}
#endif

#ifdef hackpack
\subsection{Prim's Algorithm}
#endif
\acmlisting[label=Cowconnection Example Solution, caption=Cowconnection Example Solution]{./algorithms/prims-algorithm/problems/cowconnection/cowconnection.cpp}
#ifdef hackpack
\subsubsection{Lessons Learned}
\begin{itemize}
	\item Typedefs can greatly improve readability of code
	\item Convenience classes can greatly improve readability
	\item Directed graphs can be converted to undirected graphs by inserting the edge for both the source and the destination.
\end{itemize}
#endif

