\section{Hash Window Approaches}\index{hashing}\index{hash windows}
Hashing is a mapping of objects to bytes.
These bytes are often stored in Strings or numeric data types.
Normally, hash functions attempt to map each object to a \textit{unique} set of bytes.
Also a \textit{slight} change in the object should cause a \textit{large} change in the output.
When two objects map to the same set of bytes, it is referred to as a hash collision.

\subsection{Approaches}
\begin{itemize}
	\item Identify substrings quickly and cleanly.
	\item Hash collisions to detect certain features of the input.
\end{itemize}

\subsection{Fine Print Returns!}
The cows have prepared another legal document for Farmer John to review.

The Cows are still championing the installation of an Olympic style swimming pool.
However, this time Farmer John only cares about how many times, `pool' appears in the text.

Help Farmer John determine how many times the text `pool' appears in the document.

\subsubsection{Input}
\begin{itemize}
	\item A stream of text terminated by an EOF representing the legal agreement
\end{itemize}

\subsubsection{Sample Input}
\lstinputlisting[label=Fine Print Sample Input, caption=Fine Print Sample Input]{./approaches/hash-window/problems/fine-print/fine-print.in}

\subsubsection{Output}
\begin{itemize}
	\item 1 integer representing the number of references to the word pool in the text.
\end{itemize}

\subsubsection{Sample Output}
\lstinputlisting[label=Fine Print Sample Output, caption=Fine Print Sample Output]{./approaches/hash-window/problems/fine-print/fine-print.out}

\subsubsection{Sample Solution}
\lstinputlisting[label=Fine Print Sample Solution, caption=Fine Print Sample Solution]{./approaches/hash-window/problems/fine-print/fine-print.cpp}

\subsubsection{Lessons Learned}
\begin{itemize}
	\item There is often more than one way to solve a problem,  checkout the KMP string matching algorithm for another way to solve this problem.
\end{itemize}
