\section{Breath First Search}\index{breath first search}
This algorithm is a search method for a graph or tree. 
The most common usage for bfs on a graph is when the search is limited to two operations. 
The first operation is to visit and inspect a node on a graph or tree.
The second operation is to access the neighbouring nodes of the currently visited node.
The bfs search method executes a layered traversal from the fist node.
When the method is executed bfs will examine the root node then traverse down to the left child node.
Then bfs will examine the left child node, and return to the root node.
The method will then traverse down to the right child node of the root node, examine the node and return to the root node again.
The directional left to right search pattern followed by incrementing depth from the root node continues until every node at the current depth is examined.
The bfs method on a graph works similarly however the use of a data structure to track visited nodes is needed.
The bfs method implemented on a graph will also require edges and vertices to be defined or the search will be less efficient. 

  

\subsection{BFS Graph}
BFS Graph 
\acmlisting[caption = DFS Graph, label = DFS Graph]{./algorithms/breath-first-search/examples/bfs-graph/graph-traversals.h}

\subsection{BFS Graph Input}
BFS Input
\acmlisting[caption = DFS Input, label = DFS Input]{./algorithms/breath-first-search/examples/bfs-graph/breath-first-search.in}

\subsection{BFS Graph Output}
BFS Output
\acmlisting[caption = DFS Output, label = DFS Output]{./algorithms/breath-first-search/examples/bfs-graph/breath-first-search.out}

\subsection{BFS Tree}
BFS Tree with all traversals 
\acmlisting[caption = DFS Tree, label = DFS Tree]{./algorithms/breath-first-search/examples/bfs-tree/tree-search.h}

\subsection{BFS Tree Input}
BFS Input
\acmlisting[caption = DFS Input, label = DFS Input]{./algorithms/breath-first-search/examples/bfs-tree/input.in}

\subsection{BFS Tree Output}
BFS Output
\acmlisting[caption = DFS Output, label = DFS Output]{./algorithms/breath-first-search/examples/bfs-tree/output.out}

